Preregistration

### 2019-05-05 analysis/survey/preregistration.Rmd
Initial foray into describing 2nd and 3rd set of "hypotheses"

Because of the nature of our statistical methods, we do not have exact hypotheses for the second and third set of questions. We describe how we answer these questions in the "Follow-up analyses" section below.

@@

TODO: Are there any others we should collapse?

COMMENT: See comment for Indices.

@@

We will run the upper level of our model using these sets of covariates: (TODO)

- Public affairs stuff: `donation preferences ~ public affairs knowledge + public affairs trust + public affairs activity`
- Ideology: `donation preferences ~ political ideology + social ideology + (religiosity?)`
- Charity and voluntarism: `donation preferences ~ charity trust + charity activity + volunteer activity + activism activity + association membership`
- Demographics: `donation preferences ~ gender + marital status + education + income + race + age`
- Kitchen sink model??: `donation preferences ~ EVERYTHING??`

@@

NOTE: Here's a preregistration from another Bayesian hierarchical multinomial logit for reference: <https://osf.io/u43yg>

COMMENT: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity. This should be the motivation of the collapses specified in Transformations.

We will examine the aggregate marginal posterior distributions of the attribute levels and utilize 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0. Similarly, marginal posterior distributions are "significantly" different if the 95% credible intervals don't overlap.

@@

NA.

>>>>

Because of the nature of our statistical methods, we do not have exact hypotheses for the second and third set of questions. We describe how we answer these questions in the "Follow-up analyses" and "Exploratory analysis" sections below.

@@

@@

We will run the upper level of our model using these sets of covariates:

- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs trust + Public affairs activity`
- Ideology: `Dnation preferences ~ Political ideology + Social ideology + Religiosity`
- Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
- Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`

We will also include these groups of variables simultaneously as we check the performance of different models:

- `Donation preferences ~ Public affairs + Ideology`
- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism`
- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism + Demographics`

@@

We will examine the aggregate marginal posterior distributions of the attribute levels and use 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0. Similarly, marginal posterior distributions are "significantly" different if the 95% credible intervals don't overlap.

@@
